### 2020-03-31 papers.tex
Add late arrival paper
Assign new reviews to papers
papers.tex: Retitle the ToC to avoid jokes considered insensitive in some chiefly elderly circles
Add a special-purpose review
Jim is rustling my jamesies

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{Table of COVID-tense}

@@

\addtrack
	{}{Programming Languages}
\addpaper
	{Ntinuation copassing style}
	{Cameron Wong, Dez Reed}
	{Keywords: continuation, ntinuation, control flow, programming languages}
	{SIGBOVIK_2020_paper_33}
	{0cm}
	{}
\addpaper
	{Formulating the syntactically simplest programming language}
	{Brendon Boldt}
	{Keywords: proramming languages, compilers, formal grammars}
	{SIGBOVIK_2020_paper_12}
	{0cm}
	{}
\addpaper
	{Type-directed decompilation of shell scripts}
	{Spencer Baugh, Dougal Pugson}
	{Keywords: partial evaluation, type systems, shell scripting}
	{SIGBOVIK_2020_paper_25}
	{0cm}
	{}
\addpaper
	{Verified proof of P=NP in the Silence theorem prover language}
	{Matias Scharager}
	{Keywords: soundness, P=NP, theorem prover, Silence, programming language theory, type theory}
	{SIGBOVIK_2020_paper_29}
	{0cm}
	{}

\addtrack
	{}{Systems}
\addpaper
	{SIGBOVIK '75 technical note: Conditional move for shell script acceleration}
	{Dr.\@ James McCann, Dr.\@ Tom Murphy VII}
	{Keywords: cond-, itional, move}
	{SIGBOVIK_2020_paper_32}
	{0cm}
	{}
\addpaper
	{NaN-gate synthesis and hardware deceleration}
	{Cassie Jones}
	{Keywords: hardware deceleration, hardware synthesis, electronic design automation, IEEE-754, NaN-gates, cat meme}
	{SIGBOVIK_2020_paper_19}
	{0cm}
	{}
\addpaper
	{hbc: A celebration of undefined behavior}
	{Andrew Benson}
	{Keywords: compilers, undefined behavior, Bash misuse, computer music, Principles of Imperative Computation}
	{SIGBOVIK_2020_paper_34}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_3}{0cm}

\addtrack
	{}{Theory}
\addpaper
	{A polynomial-time SAT algorithm}
	{Anonymous Author(s)}
	{Keywords: theoretical computer science, complexity theory, p versus np}
	{SIGBOVIK_2020_paper_2}
	{0cm}
	{}
\addpaper
	{Empire Machines and beyond}
	{Dar\'io de la Fuente Garc\'ia, F\'elix \'Axel Gimeno Gil, Juan Carlos Morales Vega}
	{Keywords: finite-state machines, models of computation, Empire Machines, doing research like this is awesome, Civilization XXIV (when it comes out)}
	{SIGBOVIK_2020_paper_16}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_8}{0cm}
\addpaper
	{Artificial General Relativity}
	{Pablo Samuel Castro}
	{Keywords: physics, artificial, general relativity, quantum physics, universe-changing, new science, field equations, black holes}
	{SIGBOVIK_2020_paper_14}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_5}{0cm}
\addpaper
	{Making explicit a constant appearing in an impossible equation of Carl and Moroz}
	{Matthew Weidner}
	{Keywords: computational mathematics, Hilbert's tenth problem, Diophantine sets}
	{SIGBOVIK_2020_paper_8}
	{0cm}
	{}

@@

\addtrack
	{}{Blockchain Gang}
\addpaper
	{RegisToken}
	{Irene Lin, Arnaud Avondet, Preston Vander Vos}
	{Keywords: blockchain, Ethereum, token, FCE, course registration}
	{SIGBOVIK_2020_paper_10}
	{0cm}
	{}

@@

\addtrack
	{}{Serious Business}
\addpaper
	{The SIGBOVIK 2020 field guide to plants}
	{Jim McCann (editor)}
	{Keywords: field guide, plants, to}
	{SIGBOVIK_2020_paper_31}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_12}{0cm}
\addpaper
	{Deep industrial espionage}
	{Samuel Albanie, James Thewlis, Sebastien Ehrhardt, Jo\~ao F.\@ Henriques}
	{Keywords: late, very late, so extremely late}
	{SIGBOVIK_2019_paper_43}
	{1.8cm}
	{}
\addpaper
	{What is the best game console?: A free-market--based approach}
	{Dr.\@ Tom ``I Only Write Chess Papers Now'' Murphy VII Ph.D.}
	{Keywords: invisible hand, handheld console, minimum of 3 keywords}
	{SIGBOVIK_2020_paper_30}
	{0cm}
	{}

>>>>

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{Blindsight is 2020}

@@

\addtrack
	{}{Programming Languages}
\addpaper
	{Ntinuation copassing style}
	{Cameron Wong, Dez Reed}
	{Keywords: continuation, ntinuation, control flow, programming languages}
	{SIGBOVIK_2020_paper_33}
	{0cm}
	{}
\addpaper
	{Formulating the syntactically simplest programming language}
	{Brendon Boldt}
	{Keywords: proramming languages, compilers, formal grammars}
	{SIGBOVIK_2020_paper_12}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_14}{0cm}
\addpaper
	{Type-directed decompilation of shell scripts}
	{Spencer Baugh, Dougal Pugson}
	{Keywords: partial evaluation, type systems, shell scripting}
	{SIGBOVIK_2020_paper_25}
	{0cm}
	{}
\addpaper
	{Verified proof of P=NP in the Silence theorem prover language}
	{Matias Scharager}
	{Keywords: soundness, P=NP, theorem prover, Silence, programming language theory, type theory}
	{SIGBOVIK_2020_paper_29}
	{0cm}
	{}

\addtrack
	{}{Systems}
\addpaper
	{SIGBOVIK '75 technical note: Conditional move for shell script acceleration}
	{Dr.\@ Jim McCann, Dr.\@ Tom Murphy VII}
	{Keywords: cond-, itional, move}
	{SIGBOVIK_2020_paper_32}
	{0cm}
	{}
\addpaper
	{NaN-gate synthesis and hardware deceleration}
	{Cassie Jones}
	{Keywords: hardware deceleration, hardware synthesis, electronic design automation, IEEE-754, NaN-gates, cat meme}
	{SIGBOVIK_2020_paper_19}
	{0cm}
	{}
\addpaper
	{hbc: A celebration of undefined behavior}
	{Andrew Benson}
	{Keywords: compilers, undefined behavior, Bash misuse, computer music, Principles of Imperative Computation}
	{SIGBOVIK_2020_paper_34}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_3}{0cm}

\addtrack
	{}{Theory}
\addpaper
	{A polynomial-time SAT algorithm}
	{Anonymous Author(s)}
	{Keywords: theoretical computer science, complexity theory, p versus np}
	{SIGBOVIK_2020_paper_2}
	{0cm}
	{}
\addpaper
	{Empire Machines and beyond}
	{Dar\'io de la Fuente Garc\'ia, F\'elix \'Axel Gimeno Gil, Juan Carlos Morales Vega}
	{Keywords: finite-state machines, models of computation, Empire Machines, doing research like this is awesome, Civilization XXIV (when it comes out)}
	{SIGBOVIK_2020_paper_16}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_8}{0cm}
\addpaper
	{Artificial General Relativity}
	{Pablo Samuel Castro}
	{Keywords: physics, artificial, general relativity, quantum physics, universe-changing, new science, field equations, black holes}
	{SIGBOVIK_2020_paper_14}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_5}{0cm}
\addpaper
	{Lower gauge theory: Dead duck or phoenix?}
	{Oscar I.\@ Hernandez}
	{Keywords: mathematical physics, category theory, ToE, quantum gravity, mathematical economics, marginal analysis}
	{SIGBOVIK_2020_paper_40}
	{0cm}
	{}
\addpaper
	{Making explicit a constant appearing in an impossible equation of Carl and Moroz}
	{Matthew Weidner}
	{Keywords: computational mathematics, Hilbert's tenth problem, Diophantine sets}
	{SIGBOVIK_2020_paper_8}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_16}{0cm}

@@

\addtrack
	{}{Blockchain Gang}
\addpaper
	{RegisToken}
	{Irene Lin, Arnaud Avondet, Preston Vander Vos}
	{Keywords: blockchain, Ethereum, token, FCE, course registration}
	{SIGBOVIK_2020_paper_10}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_17}{0cm}

@@

\addtrack
	{}{Serious Business}
\addpaper
	{The SIGBOVIK 2020 field guide to plants}
	{Jim McCann (editor)}
	{Keywords: field guide, plants, to}
	{SIGBOVIK_2020_paper_31}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_12}{0cm}
\addreview{SIGBOVIK_2020_review_18}{0cm}
\addpaper
	{Deep industrial espionage}
	{Samuel Albanie, James Thewlis, Sebastien Ehrhardt, Jo\~ao F.\@ Henriques}
	{Keywords: late, very late, so extremely late}
	{SIGBOVIK_2019_paper_43}
	{1.8cm}
	{}
\addpaper
	{What is the best game console?: A free-market--based approach}
	{Dr.\@ Tom ``I Only Write Chess Papers Now'' Murphy VII Ph.D.}
	{Keywords: invisible hand, handheld console, minimum of 3 keywords}
	{SIGBOVIK_2020_paper_30}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_15}{0cm}
